Towards planning of infantile cardiac surgery based on simulation

### 2012-02-24 Doc/Miccai/miccai2012.tex
extending the points we want to cover
git-svn-id: svn+ssh://scm.gforge.inria.fr/svnroot/sofa-shells@329 7b2761c9-2758-49ef-8c29-9c9f1e1aad1b

\begin{abstract}
\end{abstract}

@@

\section{Blood Vessel Model}

Thin shell model

Eq. showing rest position stuff

Fullfills requirements + collision

Test with tube + convergence

@@

surgical low-level tasks done with rest position trick (joining, patch, complex cutting/suturing)

>>>>

\begin{abstract}
% TODO
\end{abstract}

@@

\section{Blood Vessel Model} % {{{

Thin shell model
\begin{itemize}
  \item based on mechanics of continuum and shell theory
  \item used in physics for deformation modelling
  \item briefly, refer to some textbook
\end{itemize}

\noindent Eq. showing dependence on rest position:
simple $\myvec{f} = K(\myvec{x} - \myvec{x_0})$

\noindent Fulfills requirements + collision
\begin{itemize}
  \item we need deformations: like bending and twisting
  \item deformation should be global
  \item should allow arbitrary models and not rely e.g. on tubular
  structure (like \cite{Li2009})
  \item the model has to be able to deal with collisions (e.g. between AA
  and PA)
\end{itemize}

\noindent Test with tube + convergence
\begin{itemize}
  \item experimented with Olivier's model \cite{Comas2010b,Comas2010c} and
  our own model, in principle the shell implementation is not that
  important
  \item geometrical tool, independence on physical parameters -- E
\end{itemize}

% }}}

@@

\noindent surgical low-level tasks done with rest position trick (joining, patch, complex cutting/suturing)
\begin{itemize}
  \item describe the particular tasks and show that the essence is the same,
  \item describe our method with all the tricks
  \item include a schematic illustration
\end{itemize}
